### 2022-05-31 main/chapter_2ljets.tex
dzero command

>>>>

Events appearing in a region with minimal background is evidence in favour
of new contributions, and that only strengthens as the background approaches
zero.
For example, the top quark was observed by \dzero\ using seven regions all with
background expectations of $1$ or less, for a total of $3.79\pm0.55$ expected
and $17$ observed~\cite{abachi1995observation}.
If they could do that with technology from the year $1995$, we can do it now.
